\chapter{Abstract Exchange Economies}
\section{Pareto Efficient Allocations}
\begin{proposition}[Negishi Theorem] 
\\
\noindent (If) Let $\mathbb{U} = \{U \in \mathbb{R}^I | U \leq U(x) \text{ for some } x \in \mathbb{R}^{LI} \text{ such that } \sum_i x_i \leq \tilde{w} \}$
be a convex set. 
Let $x$ be a Pareto efficient allocation. 
Then there exists $\alpha \in \mathbb{R}_{+}^I$ and $\alpha \neq 0$ such that $x$ is the solution to the following problem:%
\footnote{
    In other words, there exists a Pareto weights that can justify the allocation.
}
\begin{align*}
    \max_x \ & \sum_i \alpha_i U_i(x_i) \\ 
    \text{ subject to } & \ \sum_i x_i \leq \tilde{w}
\end{align*}

\noindent (Only if) Given $\alpha \in \mathbb{R}_{+}^I$ and $\alpha \neq 0$, if $x$ is the solution to the Negishi Probelm, 
then $x$ is Pareto Optimal.
\end{proposition}

\paragraph{Proof}
(If) 
Because $\mathbb{U}$ is convex and nonempty, and $U(x) \in \text{brdy}(\mathbb{U})$,
by supporting hyperplane theorem, there exists $\alpha$ such that 
$\alpha U(x) \geq \alpha U'$ for all $U' \in \mathbb{U}$.
Hence, $x = \text{argmax}_{x'} \sum_i \alpha_i U_i(x_i')$. 
In addition, $\mathbb{U}$ is unbounded from below, we have $\alpha \in \mathbb{R}^I_+$. 


(Only if) Suppose $\alpha \in \mathbb R^I_{++}$ and $x$ solves the Negishi problem. 
Suppose, toward a contradiction, that $x$ is not Pareto optimal. Then there exists a feasible allocation $x'$ such that
\[
U_i(x_i') \geq U_i(x_i)\quad \forall i,
\]
with strict inequality for some $j$. Since $\alpha_j>0$, we have
\[
\sum_i \alpha_i U_i(x_i')
>
\sum_i \alpha_i U_i(x_i),
\]
contradicting the optimality of $x$ in the Negishi problem. Therefore, $x$ is Pareto optimal.

\(\blacksquare\)


\section{Welfare Analysis}
\begin{proposition}[First Welfare Theorem]
    In an abstract exchange economy characterized by $w \in \mathbb{R}^{S+1}_{++}$, 
    any competitive equilibrium allocation $x \in \mathbb{R}^{S+1}_{+}$
    is Pareto efficient.
\end{proposition}

\noindent \textbf{Proof:} We prove by contradiction. 
Suppose there exists $y$ that Pareto dominates $x$, then 
$y^i \succeq_P x^i \forall i$,
and  
$y^j \succ_P x^j$ for some $j$.
Then by the Walras Law and the Law of Revealed Prferences, we have 
\[
p_0 (y^i_0 - w^i_0) + \sum_s p_s (y^i_s - w^i_s) \geq p_0 (x^i_0 - w^i_0) + \sum_s p_s (x^i_s - w^i_s) = 0, \quad \text{ and }
\]
\[
p_0 (y^j_0 - w^j_0) + \sum_s p_s (y^j_s - w^j_s) > p_0 (x^j_0 - w^j_0) + \sum_s p_s (x^j_s - w^j_s) = 0
\]
Summing over $i$ (i.e., summing the two equations above), we have 
\[
p_0 \sum_i (y^i_0 - w^i_0) + \sum_s p_s \sum_i (y^i_s - w^i_s) > 0
\]
Since $p_0, p_s$ are strictly positive, 
there exists an $s$ such that
\[
\sum_i (y^i_s - w^i_s) > 0,
\]
which implies that $y$ is not feasible. \(\blacksquare\)

\textcolor{blue}{The converse of the First welfare theorem is the Second welfare theorem below.}
\noindent \textbf{Interpretation:}
In words, the Second Welfare Theorem states that 
any Pareto efficient allocation can be decentralized as a competitive equilibrium via 
transfer (equivalently, redistribution of initial endowment, where the transferred endowment 
$\Delta w^i = \frac{T_i}{p}$) --- See MWG Figure 15.b.13 for an illustration.

\begin{proposition}[Second Welfare Theorem]
    For any economy characterized by $\tilde{w} \in \mathbb{R}^{L}_{++}$, 
    any Pareto efficient allocation $x \in \mathbb{R}^{LI}_{+}$
    can be decentralized as a competitive equilibrium via price, $p \in \mathbb{R}^L_{++}$,
    of the economy $w \in \mathbb{R}_{++}^{LI}$, such that $\sum_i w_i = \tilde{w}$.
\end{proposition}

\noindent \textbf{Proof} 
Remark: The key of the proof is a separating hyperplane argument.
\\
\noindent 
Let $x \in \mathbb{R}^{LI}_{++}$ be a Pareto Efficient allocation.
Choose $w = x$.
Define the strict upper contour set for agent $i$, 
\[
B^i(x_i) := \{y_i \in \mathbb{R}^L_{+}: U(y_i) > U(x_i) \}
\]
Define the aggregate strict upper contour set as 
\[
B(x) := \bigg\{\sum_i y_i \in \mathbb{R}^L_{+}: y_i \in B^i(x_i) \forall i \bigg\}
\]
Since $B^i(x_i)$ is convex, the aggregate upper contour set is also convex. 
In addition, by Supporting Hyperplane theorem, 
there exists a nonzero price vector $p$, such that
\[
\inf_{a \in B(x)} p a \geq p \sum_i x_i
\]
We will use this equation to establish that 
\begin{itemize}
    \item[(1)] $p \in \mathbb{R}^{L}_{++}$, and 
    \item[(2)] under such price, no individual will trade.
\end{itemize}

\noindent \textbf{Part 1.}
Suppose there exists some $l$ such that $p_l < 0$, 
let 
\[
y_k^i = \begin{cases}
    x_k^i + \delta  \quad &\text{ if } k = l \\
    x_k^i \quad & \text{ if } k \neq l \\
\end{cases}
\]
Then, $p y^i < p x^i$ and $y^i \in B^i(x^i)$. 
Summing across agents, we have a contradtion to the supporting hyperplane condtion above.


Now suppose there exists some $l$ such that $p_l = 0$, 
let 
\[
y_k^i = \begin{cases}
    x_k^i + \delta  \quad &\text{ if } k = l \\
    x_k^i - \epsilon \quad & \text{ if } k \neq l \\
\end{cases}
\]
where $\delta$ is sufficiently large and $\epsilon$ is sufficiently small, 
so that the loss in $k \neq l$ can be compensated. 
Then, $p y^i < p x^i$ and $y^i \in B^i(x^i)$. 
Summing across agents, again, we have a contradiction to the supporting hyperplane condtion above.


\noindent \textbf{Part 2.} 
Finally, we prove that under $p$ found by the supporting hyperplane theorem, 
the equilibrium is autarky.
Suppose there is a strictly profitable deviation from $x^i$ for agent $i$,
namely, 
\[
\exists \tilde{x}^i, \quad \text{s.t. } p \tilde{x}^i < p x^i \quad \text{ and } \quad 
\tilde{x}^i \in B^i(x^i)
\]
Denote the payoff from the deviation by $\delta := p x^i - p \tilde{x}^i > 0$.
Pick $\tilde{x}^i + \sum_{j \neq i } y^j \in B(x)$, and apply the SHT, to obtain
\[
p \left(\tilde{x}^i + \sum_{j \neq i } y^j \right) \geq p \sum_i x^i 
\] 
It follows that 
\[
p \left(  \sum_{j \neq i } y^j  - x^j \right) \geq \delta > 0 
\]
However, consider $y^j = x^j + \epsilon$, 
we have 
$\lim p y^j = \lim p x^j$ as $\epsilon \rightarrow 0$,
a contradiction. 
Hence, it cannot exist any profitable deviation for any agent $i$. 
\(\blacksquare\)


\section{Existence Proof by Debreu's Map}
\noindent \textbf{Statement:} A competitive equilibrium exists for any economy $\omega \in \mathbb{R}_{++}^{LI}$ \\

\noindent \textbf{Proof} \\
Let $p \in \Delta^L$, $z: \text{Int}(\Delta^L) \rightarrow \mathbb{R}^L$,
and $f: \Delta^L \rightarrow 2^{\Delta^L}$ defined as follows. (This is Debreu's Map):
\begin{align*}
    f(p) = \begin{cases}
        \text{argmax}_q q z(p) \quad & \text{ if } p \in \text{int}(\Delta^L) \\ 
         \{q \in \Delta^L: p q = 0 \}\quad & \text{ if } p \in \text{bdry}(\Delta^L)
    \end{cases}
\end{align*}
This map implies that if there exists a fixed point, $p^*$
then we have $z(p^*) = 0$ and $p^* \in \text{int}{\Delta^L}$.
It remains to proof the existence of the fixed point.
We can finish the proof by the Kakutani Fixed Point Theorem, 
because $\Delta^L$ is non-empty, convex, and compact.
In addition, $f(p)$ is non-empty as it maps $p$ to either the interior or the boundary. 
$f(p)$ is also convex valued. 
Finally, by examing the following three cases, we can show that $f(p)$ is upper hemicontinous.
\begin{enumerate}
    \item $p^n \in \text{Int}(\Delta^L) \rightarrow p \in \text{Int}(\Delta^L)$
    \item $p^n \in \text{bdry}(\Delta^L) \rightarrow p \in \text{bdry}(\Delta^L)$
    \item $p^n \in \text{Int}(\Delta^L) \rightarrow p \in \text{bdry}(\Delta^L)$
\end{enumerate}

By the Kakutani FPT, there exists $p^* \in f(p^*)$.
\textit{Q.E.D.}






\section{Sufficient conditions for the uniqueness of competitive equilibrium}
Existence of a competitive equilibrium holds under general conditions, but uniqueness requires strong restrictions. Proposition 6 of the notes provides three sufficient conditions:

\begin{enumerate}
    \item \textbf{Pareto-efficient endowments.} If $\omega$ is Pareto efficient, the unique equilibrium is autarchic ($x^i = \omega^i$ for all $i$), since there are no gains from trade and strict convexity of preferences pins down the allocation on the budget line.
    
    \item \textbf{Identical, homothetic preferences.} If all agents share the same homothetic $U^i$, then $x^i(p, y^i) = y^i \, x(p, 1)$ aggregates linearly, so the economy admits a representative agent owning $\sum_i \omega^i$, and equilibrium prices depend only on aggregate endowments.
    
    \item \textbf{Gross substitutes.} If aggregate excess demand satisfies
    \begin{align*}
        p'_l > p_l \text{ and } p'_j = p_j \ \forall j \neq l \implies z_j(p') > z_j(p),
    \end{align*}
    then raising prices coordinate-by-coordinate from one candidate equilibrium $p$ to another $p'$ contradicts $z(p) = z(p') = 0$.
\end{enumerate}

\textbf{Caveat.} These conditions are sufficient but not necessary; by the Sonnenschein--Mantel--Debreu theorem, aggregate excess demand can take essentially any shape, so multiple equilibria are generic absent such restrictions.


\section{Sonnenschein-Debreu-Mantel Theorem (Anything-goes)}
The following famous theorem is known as the ``anything-goes'' theorem and Indeterminacy Theorem, 
in the sense that,
one can take ``any'' arbitrary aggregate excess demand function ($z$), 
and construct an economy with rational individuals that matches it.
This proves that individual rationality imposes no restrictions on the aggregate market behavior.
This undertermineness at the macro level outcomes leads to a famous quote by Tom Sargent:
\begin{tcolorbox}
    \quad ``The real problem in economics is not that our models impose too many restrictions on the data, but far too few''.
\end{tcolorbox}
Jesús Fernández-Villaverde says: SMD teaches us that meaningful economic predictions require disciplined structure beyond individual rationality.



\begin{proposition}[Sonnenschein-Debreu-Mantel Theorem]
    Let $\Delta_\epsilon^{L-1}$ be a trimmed simplex, with $\epsilon > 0$. 
    Given any continuous function $z : \Delta_\epsilon^{L-1}$
    satisfying continuity and Walras law,
    then there is an economy with $U^i: \mathbb{R}^L_{+} \rightarrow \mathbb{R}$, 
    $\omega \in  \mathbb{R}^{LI}_{++}$, $I \geq L$, 
    whose aggregate excess demand function, restricted to $\Delta_\epsilon^{L-1}$, equals $z$.
\end{proposition}

